---
title: "ECO528 Project 1"
author: "T.A. Meraxa"
date: "November 20, 2015"
output: html_document
---
***
###1-1 
Using the price series, calculate the simple and log monthly returns. Compare your result with holding period return and holding period return without dividends, are they different or similar? Why?

#### Load data to R
```{r, eval=FALSE}
setwd("C:/Users/T.Arcky/Dropbox/PhD_Projects/Personal Development/Coursera Finance/ECO528 Empirical Methods in Financial Economics/ECO528_Empirical_Methods_in_Finance/Project-1")

IBM <- read.csv("IBM.txt", sep = "", header = FALSE)
names(IBM) <- c("permno","date", "prc", "ret", "retx", "sprtrn")

AAPL <- read.csv("AAPL.txt", sep = "", header = FALSE)
names(AAPL) <- c("permno","date", "prc", "ret", "retx", "sprtrn")

SnP <- IBM$sprtrn
```

#### Compute
```{r, eval=FALSE}
# Calculate monthly return on IBM

# Creating nrow for IBM, AAPL
nIBM <- nrow(IBM)
nAAPL <- nrow(AAPL)


# Calculate simple monthly returns for IBM and AAPL
IBM_ret <- (IBM[2:n,3] - IBM[1:(n-1),3]) / IBM[1:(n-1),3]
AAPL_ret <- (AAPL[2:n,3] - AAPL[1:(n-1),3]) / AAPL[1:(n-1),3]

# Calculate log monthly returns for IBM and AAPL
IBM_ccret <- log(IBM[2:n,3])-log(IBM[1:(n-1),3])
AAPL_ccret <- log(AAPL[2:n,3])-log(AAPL[1:(n-1),3])
```
***
###1-2
You estimate a regression of the form given by (3.52) below in order to evaluate the effect of various firm-specific factors on the returns of a sample of firms. You run a cross-sectional regression with 200 firms
```{r, eval=FALSE}
# ri = β0 + β1 Si + β2MBi + β3PEi + β4BETAi + ui
```

You obtain the following results (with standard errors in parentheses)

```{r, eval=FALSE}
# rˆi = 0.080 + 0.801Si + 0.321MBi + 0.164PEi − 0.084BETAi
#     (0.064) (0.147)    (0.136)    (0.420)    (0.120)

# Where: 
# ri is the percentage annual return for the stock
# Si is the size of firm i measured in terms of sales revenue
# MBi is the market to book ratio of the firm
# PEi is the price/earnings (P/E) ratio of the firm  
# BETAi is the stock’s CAPM beta coefficient
```

* Calculate the t-ratios. What do you conclude about the effect of each variable on the returns of the security? On the basis of your results, what variables would you consider deleting from the regression? 
* If a stock’s beta increased from 1 to 1.2, what would be the expected effect on the stock’s return? Is the sign on beta as you would have expected? Explain your answers in each case.
    
### Answer
The t-ratios are calculated by dividing the coefficient estimate by its standard error, and round to 2 digits. 

The beta coefficients 

  



